Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
edits for 1-3

While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author. Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, under failures and as the network evolves.

>>>>

While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author. Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, both when failures occur and as the network evolves.
